Predicting Survival Probability of NASA Aircraft Engines

### 2025-04-22 slides.qmd
Slide updates 4/22

-   Survival Function: $S(x) = \int_{x}^{\infty} f(x)dx$

-   Hazard Function:
    $h(x) = \lim\limits_{\Delta x \rightarrow 0} \frac{P[x \leq X < x + \Delta x|X \geq x]}{\Delta x}$

@@

-   The data was then merged together to make one grouped dataset

@@

kable(head(temp, n = 5), format = "markdown", caption = 'NASA Aircraft Engine Data')
```

@@

autoplot(km_fit) + theme_bw()
```
:::

@@

plot_model(cox1.1,
           dot.size = 2,
           line.size = 1,
           colors = "red")+
  theme_bw()+
  labs(title = "Estimated Effects of Covariates on Hazard Ratios")+
  ylab(label = "Covariates")+
  xlab(label = "Estimated Effect on Hazard Ratio")
```

@@

par(mfrow = c(4,4),
      mar = c(2,2,4,1))

plot(data_grouped$os1, martingale, main = "Martingale Residuals: os1")
abline(h = 0, col = "red")

plot(data_grouped$os2, martingale, main = "Martingale Residuals: os2")
abline(h = 0, col = "red")

plot(data_grouped$os3, martingale, main = "Martingale Residuals: os3")
abline(h = 0, col = "red")

plot(data_grouped$sm1, martingale, main = "Martingale Residuals: sm1")
abline(h = 0, col = "red")

plot(data_grouped$sm2, martingale, main = "Martingale Residuals: sm2")
abline(h = 0, col = "red")

plot(data_grouped$sm3, martingale, main = "Martingale Residuals: sm3")
abline(h = 0, col = "red")

plot(data_grouped$sm4, martingale, main = "Martingale Residuals: sm4")
abline(h = 0, col = "red")

plot(data_grouped$sm5, martingale, main = "Martingale Residuals: sm5")
abline(h = 0, col = "red")

plot(data_grouped$sm6, martingale, main = "Martingale Residuals: sm6")
abline(h = 0, col = "red")

plot(data_grouped$sm7, martingale, main = "Martingale Residuals: sm7")
abline(h = 0, col = "red")

plot(data_grouped$sm8, martingale, main = "Martingale Residuals: sm8")
abline(h = 0, col = "red")

plot(data_grouped$sm9, martingale, main = "Martingale Residuals: sm9")
abline(h = 0, col = "red")

plot(data_grouped$sm10, martingale, main = "Martingale Residuals: sm10")
abline(h = 0, col = "red")

plot(data_grouped$sm11, martingale, main = "Martingale Residuals: sm11")
abline(h = 0, col = "red")

plot(data_grouped$sm12, martingale, main = "Martingale Residuals: sm12")
abline(h = 0, col = "red")

plot(data_grouped$sm13, martingale, main = "Martingale Residuals: sm13")
abline(h = 0, col = "red")

plot(data_grouped$sm14, martingale, main = "Martingale Residuals: sm14")
abline(h = 0, col = "red")

plot(data_grouped$sm15, martingale, main = "Martingale Residuals: sm15")
abline(h = 0, col = "red")

plot(data_grouped$sm17, martingale, main = "Martingale Residuals: sm17")
abline(h = 0, col = "red")

plot(data_grouped$sm18, martingale, main = "Martingale Residuals: sm18")
abline(h = 0, col = "red")

plot(data_grouped$sm20, martingale, main = "Martingale Residuals: sm20")
abline(h = 0, col = "red")

plot(data_grouped$sm21, martingale, main = "Martingale Residuals: sm21")
abline(h = 0, col = "red")
```

>>>>

@@

@@

kable(head(temp, n = 3), format = "markdown", caption = 'NASA Aircraft Engine Data')
```

@@

autoplot(km_fit) + theme_bw() + labs(y = "Survival Probability (%)", x = 'Time (Iterations)')
```
:::

@@

plot_model(cox1.1,
           dot.size = 2,
           line.size = 1,
           colors = "red")+
  theme_bw()+
  labs(title = "Estimated Effects of Covariates on Hazard Ratios",
       y = "Estimated Effect on Hazard Ratio",
       x = "Covariates")
```

@@

par(mfrow = c(4,6),
      mar = c(2,2,4,1))

plot(data_grouped$os1, martingale, main = "Martingale: os1")
abline(h = 0, col = "red")

plot(data_grouped$os2, martingale, main = "Martingale: os2")
abline(h = 0, col = "red")

plot(data_grouped$os3, martingale, main = "Martingale: os3")
abline(h = 0, col = "red")

plot(data_grouped$sm1, martingale, main = "Martingale: sm1")
abline(h = 0, col = "red")

plot(data_grouped$sm2, martingale, main = "Martingale: sm2")
abline(h = 0, col = "red")

plot(data_grouped$sm3, martingale, main = "Martingale: sm3")
abline(h = 0, col = "red")

plot(data_grouped$sm4, martingale, main = "Martingale: sm4")
abline(h = 0, col = "red")

plot(data_grouped$sm5, martingale, main = "Martingale: sm5")
abline(h = 0, col = "red")

plot(data_grouped$sm6, martingale, main = "Martingale: sm6")
abline(h = 0, col = "red")

plot(data_grouped$sm7, martingale, main = "Martingale: sm7")
abline(h = 0, col = "red")

plot(data_grouped$sm8, martingale, main = "Martingale: sm8")
abline(h = 0, col = "red")

plot(data_grouped$sm9, martingale, main = "Martingale: sm9")
abline(h = 0, col = "red")

plot(data_grouped$sm10, martingale, main = "Martingale: sm10")
abline(h = 0, col = "red")

plot(data_grouped$sm11, martingale, main = "Martingale: sm11")
abline(h = 0, col = "red")

plot(data_grouped$sm12, martingale, main = "Martingale: sm12")
abline(h = 0, col = "red")

plot(data_grouped$sm13, martingale, main = "Martingale: sm13")
abline(h = 0, col = "red")

plot(data_grouped$sm14, martingale, main = "Martingale: sm14")
abline(h = 0, col = "red")

plot(data_grouped$sm15, martingale, main = "Martingale: sm15")
abline(h = 0, col = "red")

plot(data_grouped$sm17, martingale, main = "Martingale: sm17")
abline(h = 0, col = "red")

plot(data_grouped$sm18, martingale, main = "Martingale: sm18")
abline(h = 0, col = "red")

plot(data_grouped$sm20, martingale, main = "Martingale: sm20")
abline(h = 0, col = "red")

plot(data_grouped$sm21, martingale, main = "Martingale: sm21")
abline(h = 0, col = "red")
```
